WrapITK: Enhanced languages support\\ for the Insight Toolkit

### 2006-02-28 article/Article.tex
Code cleaning and re-organization
darcs-hash:20060225111055-733a7-036ae5e88e995c642252eb1b668981fc5daa5a4c.gz
add ImportCallback doc
darcs-hash:20060228161719-2fc9d-a84297098857aeac1d5cae23f341ddf4fb1c9f8f.gz

@@

\begin{itemize}
  \item \verb$BEGIN_WRAPPER_LIBRARY()$ sets up the environment to wrap a set of classes into a
library with a given name. This macro is defined in \verb$itkConfigWrapping.cmake$
\verb$WRAPPER_LIBRARY_DEPENDS$ stores the list of WrapITK libraries on which the
current library depends (e.g. which libraries wrap classes like \verb$Image$ or
\verb$SpatialObject$, that are going to be used in the current library). Every project
should at least depend on \verb$ITKCommonA$.

>>>>

\verb$itk$ module can be very long to import. The \verb$itkConfig$ module define
a \verb$ImportCallback$ method which will be called when each sub module is
imported in the import process. \verb$ImportCallback$ can be customized to report the
progress status of the import process. It must be a function that can take
the name of the library being imported as a parameter. Here is an example of a very
basic callback function which display the name of the submodule being imported on
the standard error output.
\small \begin{verbatim}
import sys, itkConfig
def stderr_callback(name):
  print >> sys.stderr, name
itkConfig.ImportCallback = stderr_callback
import itk
\end{verbatim} \normalsize

@@

\begin{itemize}
  \item \verb$BEGIN_WRAPPER_LIBRARY()$ sets up the environment to wrap a set of classes into a
library with a given name. This macro is defined in \verb$ConfigureWrapping.cmake$
\verb$WRAPPER_LIBRARY_DEPENDS$ stores the list of WrapITK libraries on which the
current library depends (e.g. which libraries wrap classes like \verb$Image$ or
\verb$SpatialObject$, that are going to be used in the current library). Every project
should at least depend on \verb$ITKCommonA$.
